Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-15 paper/paper.tex
caps
minor typesetting

This intermediate ANSI-C code model contains a specification $\phi$ for the
property of interest (i.e., robust stability) and is passed to the
Counterexample-Guided Inductive Synthesis (CEGIS) module of
CBMC~\cite{ClarkeKL04}, where the controller is marked as the input variable
to synthesize.  The properties specified in the ANSI-C code model can only
be satisfied if CEGIS synthesizes controller coefficients that
satisfy~$\phi$.  CEGIS employs an iterative, counterexample-guided
refinement process which is explained in detail in
section~\ref{synthesizer-general}.  A~successful synthesis result is
reported if CEGIS generates a controller that is safe with respect to~$\phi$. 
In particular, the ANSI-C code model guarantees that a synthesized solution
is complete and sound with respect to the stability property~$\phi$, since it
does not depend on system inputs and outputs.  In the case of stability, the
specification~$\phi$ consists in a number of assumptions on the polynomial
coefficients, following Jury's Criteria, as well as the restrictions set in
the representation of these coefficients as discussed in more detail in 
Section~\ref{synthesis-elements}.

@@

We will illustrate our approach with a classical cruise control example,
extracted from the literature~\cite{Astrom08}.  The example will allow us to
highlight the challenges that arise when using finite precision arithmetic
in digital control.  We are given a discrete plant model (with a time step
of $0.2$s), which is represented by the following $z$-expression:
%
\begin{equation}
\label{Eq:running-example-plant}
G\left(z\right) = \frac{0.0264}{z-0.9998}.
\end{equation}

Using an optimization tool, the authors
of~\cite{DBLP:conf/hybrid/WangGRJF16} have designed a high-performance
controller for this plant, which is characterized by the following
$z$-domain transfer function:
%
\begin{equation}
\label{Eq:running-example-controller}
C\left(z\right) = \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
%
The authors of~\cite{DBLP:conf/hybrid/WangGRJF16} claim that this controller
$C(z)$ (Eq.~\eqref{Eq:running-example-controller}) stabilizes the
closed-loop system for the discrete plant model $G(z)$
(Eq.~\ref{Eq:running-example-plant}).  However, if the effects of finite
precision arithmetic are considered during verification (e.g., fixed-point
arithmetic and word-length), then this closed-loop system becomes unstable.
%
For instance, an implementation of $C(z)$ using \param{4}{16} fixed-point
numbers (i.e., $4$ bits for the integer part and $16$ bits for the
fractional part) can be modeled as follows:
%
\begin{equation}
\label{Eq:running-example-controller-quantized}
\resizebox{.47\textwidth}{!}{
$C_{q}\left(z\right) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375}$
}
\end{equation} 
%
The resulting system using the typical series loop configuration, where
$C_{q}\left(z\right)$ and $G\left(z\right)$ are in the forward path, is
unstable.
%
\subsection{Program synthesis for the example}
%
We now demonstrate how our approach solves the synthesis problem for the
example given in the previous section.  We start with the candidate solution
with all coefficients zero, as given below, and a precision of $I_p=16$,
$F_p=24$.  The digital controller is designed with standard techniques for
control systems~\cite{Kuo:2002:ACS:579453, Ogata:1987:DCS:26170}.
%
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.
%
%$$
%\begin{array}{ll}
%N_C(z) {=} 0z^2{+}0z{+}0\\
%D_C(z) {=} 0z^2{+}0z{+}0\\
%\end{array}
%$$
$$ C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0} $$

>>>>

This intermediate ANSI-C code model contains a specification $\phi$ for the
property of interest (i.e., robust stability) and is passed to the
Counterexample-Guided Inductive Synthesis (CEGIS) module of
CBMC~\cite{ClarkeKL04}, where the controller is marked as the input variable
to synthesize.  The properties specified in the ANSI-C code model can only
be satisfied if CEGIS synthesizes controller coefficients that
satisfy~$\phi$.  CEGIS employs an iterative, counterexample-guided
refinement process which is explained in detail in
Section~\ref{synthesizer-general}.  A~successful synthesis result is
reported if CEGIS generates a controller that is safe with respect to~$\phi$. 
In particular, the ANSI-C code model guarantees that a synthesized solution
is complete and sound with respect to the stability property~$\phi$, since it
does not depend on system inputs and outputs.  In the case of stability, the
specification~$\phi$ consists in a number of assumptions on the polynomial
coefficients, following Jury's Criteria, as well as the restrictions set in
the representation of these coefficients as discussed in more detail in 
Section~\ref{synthesis-elements}.

@@

We will illustrate our approach with a classical cruise control example,
extracted from the literature~\cite{Astrom08}.  The example will allow us to
highlight the challenges that arise when using finite precision arithmetic
in digital control.  We are given a discrete plant model (with a time step
of $0.2$\,s), which is represented by the following $z$-expression:
%
\begin{equation}
\label{Eq:running-example-plant}
G(z) = \frac{0.0264}{z-0.9998}.
\end{equation}

Using an optimization tool, the authors
of~\cite{DBLP:conf/hybrid/WangGRJF16} have designed a high-performance
controller for this plant, which is characterized by the following
$z$-domain transfer function:
%
\begin{equation}
\label{Eq:running-example-controller}
C(z) = \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
%
The authors of~\cite{DBLP:conf/hybrid/WangGRJF16} claim that this controller
$C(z)$ (Eq.~\eqref{Eq:running-example-controller}) stabilizes the
closed-loop system for the discrete plant model $G(z)$
(Eq.~\ref{Eq:running-example-plant}).  However, if the effects of finite
precision arithmetic are considered during verification (e.g., fixed-point
arithmetic and word-length), then this closed-loop system becomes unstable.
%
For instance, an implementation of $C(z)$ using \param{4}{16} fixed-point
numbers (i.e., $4$ bits for the integer part and $16$ bits for the
fractional part) can be modeled as follows:
%
\begin{equation}
\label{Eq:running-example-controller-quantized}
\resizebox{.47\textwidth}{!}{
$C_{q}(z) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375}$
}
\end{equation} 
%
The resulting system using the typical series loop configuration, where
$C_{q}(z)$ and $G(z)$ are in the forward path, is
unstable.
%
\subsection{Program synthesis for the example}
%
We now demonstrate how our approach solves the synthesis problem for the
example given in the previous section.  We start with the candidate solution
with all coefficients zero, as given below, and a precision of $I_p=16$,
$F_p=24$.  The digital controller is designed with standard techniques for
control systems~\cite{Kuo:2002:ACS:579453, Ogata:1987:DCS:26170}.
%
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.
%
%$$
%\begin{array}{ll}
%N_C(z) {=} 0z^2{+}0z{+}0\\
%D_C(z) {=} 0z^2{+}0z{+}0\\
%\end{array}
%$$
$$ C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0} $$
